Enhance Road Detection Data Processing of LiDAR Point Clouds to Specifically Identify Unmarked Gravel Rural Roads

### 2024-07-10 Huston_Paper.tex
Oh yeah this exists

			{Arcs of 6 degrees from the first three channels of scanning LiDAR data centered directly in front of the vehicle (Fig. \ref{fig:nine_arcs_example}) were extracted and exported to a database if coincident with the manually defined areas (Fig. \ref{fig:test_vs_train_areas}). Later, nine arcs (three arcs from three channels) will be classified for the prediction of intersecting roads. Arc length was chosen based on approximate vehicle width (set to 6 degrees), and the location of each arc was fixed relative to the center line (length-wise) of the vehicle. Training data was extracted from a single arc, with approximately 28 LiDAR points per arc, from each 360 degree LiDAR scan if the arc was coincident to a manually projected 2D area. As arc is fixed to 6 degrees, the number of data points is constant, thus the only factor contributing to point density would be potential elevation changes between the vehicle and arc. This study found that the training data sparsity had a standard deviation that was distinct between LiDAR channels and similar between terrain classes in each LiDAR channel, therefore for this work LiDAR sparsity was considered a negligible issue. Raw spatial and intensity values from the coincident arc were saved to a raw training database. Separate training databases were maintained for each individual channel. Features that describe the raw spatial and intensity data were extracted. Thirty percent of the training data base was randomly selected and set aside as a validation data base. Training data was visually examined for clustering to verify that a RDF would be able to be trained (Fig. \ref{fig:training_data_cluster_2}). It was found that each class generally clustered to a certain range with some overlap, which indicates that a RDF may be trained. }

@@

			\begin{figure}[H]
				\centering
				\includegraphics[width=0.75\linewidth]{figures/test_vs_train_areas_hatch}
				\caption[Training vs Testing Areas]{Training areas were kept separate from the testing areas, shown is a close-up, top-down view of the road of interest. }
				\label{fig:test_vs_train_areas}
			\end{figure}

@@

		{Classification of real-world data outside of the training data set presents difficulties to the generated Random Decision Forest Classifiers generated in this work. Due to the side of the road being re-grassed near a portion of the asphalt road, the terrain classification algorithm struggled to differentiate the dirt from gravel, leading to some misclassification of the side-of-road areas. Examination of the feature distribution shows a high amount of overlap (Fig. \ref{fig:dirt_v_gravel}). Exploitation of confidence scores to adjust results by requiring a very high confidence for positive gravel surface classification was explored. All gravel surfaces that did not meet a 80\% confidence score was re-labeled as \textit{unknown}, however these adjustment had either a negligible or detrimental impact on the final results. Higher confidence score requirements resulted in \textit{unknown} over-classification, while too low resulted in \textit{gravel} over-classification. Overall it was found that an average true-positive accuracy of all intersecting gravel surfaces was 74.97\% (Fig. \ref{fig:prepostadjust}). If any asphalt miss-classification on the gravel areas is included, the average true-positive road detection accuracy increases to 79.18\%. It was found that an average true-positive accuracy of all asphalt surfaces was 87.05\%. Due to recent construction, discovered asphalt accuracy was artificially lowered due to the area in front of a gravel driveway being contaminated with gravel. It was found that an average of 18.55\% of asphalt areas were classified as gravel because of contamination. Differentiation between gravel road surfaces and surrounding terrain is necessary to determine boundaries for trajectory tracking and navigation. Overall average distribution for \textit{unknown} terrain class within side-of-road areas was found to be 77.94\%, which is lower than expected due to the side of the road being re-grassed. It is acknowledged by the authors that the classification algorithm must yield a result that most closely matches one of the trained classes, which led to lower accuracy scores in these circumstances. Results were compared to algorithms trained with smaller data sets in order to determine if the training data was sufficiently large for this specific scenario. Using 25\% and 50\% of total available training data yielded poor results compared to shown, however using 75\% of all available training data yielded results comparable to the shown results, indicating that the training data set is sufficient for this specific scenario. Overall discovered accuracy levels may be sufficient for the purpose of identifying asphalt and gravel roads by considering trends between classified arcs.}

>>>>

			{Arcs of 6 degrees from the first three channels of scanning LiDAR data centered directly in front of the vehicle (Fig. \ref{fig:nine_arcs_example}) were extracted and exported to a database if coincident with the manually defined areas (Fig. \ref{fig:test_vs_train_areas}). Training data area and number of LiDAR points within the area has no bearing on the amount of training data used. Later, nine arcs (three arcs from three channels) will be classified for the prediction of intersecting roads. Arc length was chosen based on approximate vehicle width (set to 6 degrees), and the location of each arc was fixed relative to the center line (length-wise) of the vehicle. Training data was extracted from a single arc, with approximately 28 LiDAR points per arc, from each 360 degree LiDAR scan if the arc was coincident to a manually projected 2D area. As each arc is fixed to 6 degrees, the number of data points is constant, thus the only factor contributing to point density would be potential elevation changes between the vehicle and arc. This study found that the training data sparsity had a standard deviation that was distinct between LiDAR channels and similar between terrain classes in each LiDAR channel, therefore for this work LiDAR sparsity was considered a negligible issue. Raw spatial and intensity values from the coincident arc were saved to a raw training database. Separate training databases were maintained for each individual channel. Features that describe the raw spatial and intensity data were extracted. Thirty percent of the training data base was randomly selected and set aside as a validation data base. Training data was visually examined for clustering to verify that a RDF would be able to be trained (Fig. \ref{fig:training_data_cluster_2}). It was found that each class generally clustered to a certain range with some overlap, which indicates that a RDF may be trained. }

@@

			\begin{figure}[H]
				\centering
				\includegraphics[width=0.75\linewidth]{figures/test_vs_train_areas_hatch}
				\caption[Training vs Testing Areas]{Training areas were kept separate from the testing areas, shown is a top-down view of the road of interest along with most of the training and testing area. Some of the training area is off-image. Training data area and number of LiDAR points within the area has no bearing on the amount of training data used.}
				\label{fig:test_vs_train_areas}
			\end{figure}

@@

		{Classification of real-world data outside of the training data set presents difficulties to the generated Random Decision Forest Classifiers generated in this work. Due to the side of the road being re-grassed near a portion of the asphalt road, the terrain classification algorithm struggled to differentiate the dirt from gravel, leading to some misclassification of the side-of-road areas. Examination of the feature distribution shows a high amount of overlap (Fig. \ref{fig:dirt_v_gravel}). Higher LiDAR point density from a higher resolution LiDAR in conjunction with more descriptive features may yield better results, however for this was outside the scope of this work. Exploitation of confidence scores to adjust results by requiring a very high confidence for positive gravel surface classification was explored. All gravel surfaces that did not meet a 80\% confidence score was re-labeled as \textit{unknown}, however these adjustment had either a negligible or detrimental impact on the final results. Higher confidence score requirements resulted in \textit{unknown} over-classification, while too low resulted in \textit{gravel} over-classification. Overall it was found that an average true-positive accuracy of all intersecting gravel surfaces was 74.97\% (Fig. \ref{fig:prepostadjust}). If any asphalt miss-classification on the gravel areas is included, the average true-positive road detection accuracy increases to 79.18\%. It was found that an average true-positive accuracy of all asphalt surfaces was 87.05\%. Due to recent construction, discovered asphalt accuracy was artificially lowered due to the area in front of a gravel driveway being contaminated with gravel. It was found that an average of 18.55\% of asphalt areas were classified as gravel because of contamination. Differentiation between gravel road surfaces and surrounding terrain is necessary to determine boundaries for trajectory tracking and navigation. Overall average distribution for \textit{unknown} terrain class within side-of-road areas was found to be 77.94\%, which is lower than expected due to the side of the road being re-grassed. It is acknowledged by the authors that the classification algorithm must yield a result that most closely matches one of the trained classes, which led to lower accuracy scores in these circumstances. Results were compared to algorithms trained with smaller data sets in order to determine if the training data was sufficiently large for this specific scenario. Using 25\% and 50\% of total available training data yielded poor results compared to shown, however using 75\% of all available training data yielded results comparable to the shown results, indicating that the training data set is sufficient for this specific scenario. Overall discovered accuracy levels may be sufficient for the purpose of identifying asphalt and gravel roads by considering trends between classified arcs.}
